Appendix 4: species distribution model comparison between INLA and sdmTMB

### 2021-12-16 doc/appendix-binomial-inla.Rmd
minor edit
remove inlabru

---
title: "Appendix 4: species distribution model comparison between inla and sdmTMB"
output:
  pdf_document:
    highlight: tango
---

@@

```{r packages, message=FALSE, warning=FALSE, cache=FALSE}
library(ggplot2)
library(dplyr)
library(sdmTMB)
library(INLA)
library(inlabru)
theme_set(ggsidekick::theme_sleek())
```

@@

Similar predictions are more complicated to extract from INLA, but can be plotted for the original sample locations.

>>>>

---
title: "Appendix 4: species distribution model comparison between INLA and sdmTMB"
output:
  pdf_document:
    highlight: tango
---

@@

```{r packages, message=FALSE, warning=FALSE, cache=FALSE}
library(ggplot2)
library(dplyr)
library(sdmTMB)
library(INLA)
# library(inlabru)
theme_set(ggsidekick::theme_sleek())
```

@@

Similar predictions are more complicated to extract from INLA, but are easy to plot for the original sample locations.
